Dusty galaxies and the degeneracy between their dust distributions and the attenuation formula

### 2016-03-18 paper.tex
Incoporated figure into paper

We perform a second test to investigate the effect of episodes of constant
star formation rate with variable duration on the dispersion about the best-fit
relation.  For each high-redshift dusty galaxy we draw a random duration from a
uniform distribution with limits at 20 Myr and 2 Gyr.  We calculate the
galaxy's UV- and IR-derived SFRs using the conversion factors for this duration.
The IR conversion factor requires a UV escape fraction from one of the given
UV escape fractions shown in Fig. \ref{spread}; we use the given UV escape
fraction which is closest to the galaxy's UV escape fraction for a duration
of 415 Myr.  We use the UV- and IR-derived SFRs to calculate UV and H$\alpha$
escape fractions for the random duration.  We perform a regression for the
sample of galaxies, record $q$, and repeat the process 10,000 times.  Fig.
\ref{} shows the distribution of $q$ values from this process.  While the
$q$ values bounding the central 50\% of the sample encompass the range of $q$
values in Fig. \ref{}, we caution that our assumption of a uniform distribution
of durations is likely incorrect.

@@

>>>>

@@

We perform a second test to investigate the effect of episodes of constant
star formation rate with variable duration on the dispersion about the best-fit
relation.  For each high-redshift dusty galaxy we draw a random duration from a
uniform distribution with limits at 20 Myr and 2 Gyr.  We calculate the
galaxy's UV- and IR-derived SFRs using the conversion factors for this duration.
The IR conversion factor requires a UV escape fraction from one of the given
UV escape fractions shown in Fig. \ref{spread}; we use the given UV escape
fraction which is closest to the galaxy's UV escape fraction for a duration
of 415 Myr.  We use the UV- and IR-derived SFRs to calculate UV and H$\alpha$
escape fractions for the random duration.  We perform a regression for the
sample of galaxies, record the $q$ value, and repeat the process 10,000 times.  Fig.
\ref{distq} shows the distribution of $q$ values.  While the
$q$ values bounding the central 50\% of the sample encompass the range of $q$
values in Fig. \ref{distq}, we caution that our assumption of a uniform
distribution of durations is likely incorrect.

\begin{figure}[!ht]
\centering
\includegraphics[scale=0.5]{dist_hauv_age.eps}
\caption{A distribution of best-fit power-law indices, $q$ values, for the
relation between H$\alpha$ and UV escape fractions for the dusty galaxies at
high redshift.  This distribution comes from drawing for each galaxy in the
sample a random duration between 20 Myr and 2 Gyr for an episode of constant
star formation rate.\label{distq}}
\end{figure}
